Web feed based content extraction with JavaScript rendering for the Invenio crawler

### 2013-10-29 tex/5-evaluation.tex
Update with graphic descriptions and compared project links.

\subsection{Content extraction}
\begin{enumerate}
  \item running time
  \item quality of output compared
\end{enumerate}

\subsection{JavaScript rendering}
\begin{enumerate}
  \item running time
\end{enumerate}

>>>>

\subsection{Content extraction}
Compare:
\begin{itemize}
  \item Our solution
  \item Boilerpipe \surl{https://github.com/misja/python-boilerpipe}
  \item Goose \surl{https://github.com/grangier/python-goose}
  \item Readability \surl{https://github.com/buriy/python-readability}
\end{itemize}
On:
\begin{enumerate}
  \item Running time
  \begin{itemize}
    \item Plot duration as a function of the page length
    \item Plot duration as a function of the number or pages (our should only take time to build the rules)
  \end{itemize}
  \item Quality of output compared:
  \begin{itemize}
    \item Chart of success pourcentages
  \end{itemize}
\end{enumerate}

\subsection{JavaScript rendering}
Compare:
\begin{itemize}
  \item "Wget crawl" \surl{http://blogforever.eu/blog/2011/05/21/creating-a-snapshot-of-a-blog-post-using-wget/}
  \item wkhtmltopdf \surl{http://code.google.com/p/wkhtmltopdf/}
  \item Selenium + full browser
  \item probably others
\end{itemize}
On:
\begin{itemize}
  \item Table comparing functionalities of each solution
  \item Histogram of redering time per browser (phantomjs/chrome/firefox)
\end{itemize}

### 2013-10-29 tex/6-conclusion-and-future-work.tex
Update with graphic descriptions and compared project links.

\section{Conclusion and Future Work}
This paragraph will end the body of this sample document.
Remember that you might still have Acknowledgments or
Appendices; brief samples of these
follow.  There is still the Bibliography to deal with; and
we will make a disclaimer about that here: with the exception
of the reference to the \LaTeX\ book, the citations in
this paper are to articles which have nothing to
do with the present subject and are used as
examples only.

>>>>

\section{Conclusion and Future Work}
\begin{itemize}
  \item Recap the problem and the objective
  \item Summarize how've solved it
  \item Mention challenges and problems
  \item Hint for future work
\end{itemize}
